---
title: "UVLT CAT + LJT Descriptive Report"
subtitle: "Workbook descriptives and visualizations"
lang: ja
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: show
    df-print: paged
execute:
  echo: false
  warning: false
  message: false
params:
  export_xlsx: ""
---

```{r}
required_packages <- c(
  "readxl", "dplyr", "tidyr", "stringr", "purrr",
  "ggplot2", "scales", "gt", "glue", "jsonlite", "forcats"
)

missing_packages <- required_packages[!vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)]

if (length(missing_packages)) {
  stop(
    paste(
      "Missing R packages:",
      paste(missing_packages, collapse = ", "),
      "\nInstall them before rendering this report."
    ),
    call. = FALSE
  )
}

suppressPackageStartupMessages({
  library(readxl)
  library(dplyr)
  library(tidyr)
  library(stringr)
  library(purrr)
  library(ggplot2)
  library(scales)
  library(gt)
  library(glue)
  library(jsonlite)
  library(forcats)
})

options(
  dplyr.summarise.inform = FALSE,
  scipen = 999
)

base_required_sheets <- c(
  "summary",
  "band_diagnostics",
  "testlet_log",
  "item_responses",
  "practice",
  "estimates",
  "session_events",
  "routing_summary",
  "linking_coeffs",
  "testlet_variance"
)

ljt_optional_sheets <- c("ljt_log", "ljt_summary", "ljt_session_meta")
band_levels <- c("1k", "2k", "3k", "4k", "5k")
condition_levels <- c("appropriate", "inappropriate")

drop_note_rows <- function(df) {
  if ("note" %in% names(df)) {
    df <- df %>% filter(is.na(note) | note != "no data")
  }
  df
}

safe_numeric <- function(x) {
  suppressWarnings(as.numeric(x))
}

parse_time <- function(x) {
  if (is.null(x)) {
    return(as.POSIXct(character()))
  }

  x <- as.character(x)
  x[x == ""] <- NA_character_
  as.POSIXct(
    x,
    tz = Sys.timezone(),
    tryFormats = c(
      "%Y-%m-%dT%H:%M:%OS",
      "%Y-%m-%d %H:%M:%OS",
      "%Y/%m/%d %H:%M:%OS"
    )
  )
}

parse_flag <- function(x) {
  if (is.logical(x)) return(x)
  x <- tolower(trimws(as.character(x)))
  case_when(
    x %in% c("true", "t", "1", "yes") ~ TRUE,
    x %in% c("false", "f", "0", "no") ~ FALSE,
    TRUE ~ NA
  )
}

fmt_num <- function(x, digits = 3) {
  ifelse(is.na(x), "NA", formatC(x, digits = digits, format = "f"))
}

fmt_pct <- function(x, digits = 1) {
  ifelse(is.na(x), "NA", percent(x, accuracy = 10^-digits))
}

fmt_int <- function(x) {
  ifelse(is.na(x), "NA", comma(round(as.numeric(x))))
}

fmt_ms <- function(x) {
  ifelse(is.na(x), "NA", glue("{fmt_int(x)} ms"))
}

fmt_min <- function(x) {
  ifelse(is.na(x), "NA", formatC(as.numeric(x) / 60000, digits = 2, format = "f"))
}

resolve_export_path <- function(path) {
  if (nzchar(path)) {
    return(normalizePath(path, winslash = "/", mustWork = TRUE))
  }

  candidates <- list.files(
    path = ".",
    pattern = "\\.xlsx$",
    recursive = TRUE,
    full.names = TRUE
  )

  candidates <- candidates[
    !grepl("reports[/\\\\]output", candidates) &
      !grepl("(^|[/\\\\])_tmp_", candidates)
  ]

  if (!length(candidates)) {
    stop(
      "No Excel workbook was found. Pass the workbook path with -P export_xlsx=/path/to/file.xlsx.",
      call. = FALSE
    )
  }

  valid_candidates <- keep(candidates, function(candidate) {
    sheets <- tryCatch(readxl::excel_sheets(candidate), error = function(e) character())
    all(base_required_sheets %in% sheets)
  })

  if (!length(valid_candidates)) {
    stop(
      "No workbook with the required UVLT export sheets was found. Pass the workbook path explicitly with -P export_xlsx=...",
      call. = FALSE
    )
  }

  info <- file.info(valid_candidates)
  normalizePath(valid_candidates[order(info$mtime, decreasing = TRUE)[1]], winslash = "/", mustWork = TRUE)
}

read_sheet <- function(sheet_name, workbook_path, sheet_names) {
  if (!(sheet_name %in% sheet_names)) {
    return(tibble())
  }
  readxl::read_excel(workbook_path, sheet = sheet_name, guess_max = 10000) %>%
    drop_note_rows()
}

export_xlsx <- resolve_export_path(params$export_xlsx)
sheet_names <- readxl::excel_sheets(export_xlsx)
missing_sheets <- setdiff(base_required_sheets, sheet_names)

if (length(missing_sheets)) {
  stop(
    paste(
      "The workbook is missing required sheets:",
      paste(missing_sheets, collapse = ", ")
    ),
    call. = FALSE
  )
}

has_ljt <- all(ljt_optional_sheets %in% sheet_names)

summary_tbl <- read_sheet("summary", export_xlsx, sheet_names) %>%
  slice(1) %>%
  mutate(
    startedAt = parse_time(startedAt),
    completedAt = parse_time(completedAt),
    across(any_of(c(
      "sessionElapsedMs", "administeredTestlets", "administeredItems",
      "plannedTestlets", "plannedItems", "targetSE", "quadraturePoints",
      "selectionThetaStep", "rawCorrect", "theta", "se", "map",
      "linkedRaschTheta", "linkedRaschSE", "estimatedVocabularySize",
      "lowerVocabularySize", "upperVocabularySize", "interruptionEvents",
      "browserBackAttempts", "unloadPrompts", "pageHiddenEvents",
      "restoreEvents", "linkingSampleSize"
    )), safe_numeric)
  )

if (!nrow(summary_tbl)) {
  stop("The summary sheet is empty.", call. = FALSE)
}

band_diag_tbl <- read_sheet("band_diagnostics", export_xlsx, sheet_names) %>%
  mutate(
    band = factor(tolower(band), levels = band_levels),
    across(any_of(c(
      "expectedAccuracy", "lowerAccuracy", "upperAccuracy", "expectedFormScore",
      "estimatedKnownWords", "lowerKnownWords", "upperKnownWords",
      "itemCount", "observedCorrect", "observedItems", "observedAccuracy",
      "meanDifficulty"
    )), safe_numeric)
  ) %>%
  arrange(band)

testlet_log_tbl <- read_sheet("testlet_log", export_xlsx, sheet_names) %>%
  mutate(
    order = safe_numeric(order),
    level = factor(tolower(level), levels = band_levels),
    across(any_of(c(
      "selectionTheta", "selectionDifficulty", "selectionRawDifficulty",
      "informationScore", "posteriorReductionScore", "difficultyGap",
      "elapsedMs", "correctCount"
    )), safe_numeric),
    across(any_of(c("selectedAt", "presentedAt", "submittedAt")), parse_time),
    accuracyRate = ifelse(is.na(correctCount), NA_real_, correctCount / 3)
  ) %>%
  arrange(order)

item_tbl <- read_sheet("item_responses", export_xlsx, sheet_names) %>%
  mutate(
    level = factor(tolower(level), levels = band_levels),
    correct = parse_flag(correct),
    across(any_of(c(
      "positionInForm", "testletVariance", "rawDifficulty", "linkedDifficulty",
      "difficulty", "thetaBefore", "thetaAfter", "seAfter",
      "thetaAfterLinkedRasch", "seAfterLinkedRasch", "testletElapsedMs"
    )), safe_numeric),
    across(any_of(c("testletPresentedAt", "responseSubmittedAt", "timestamp")), parse_time)
  )

practice_tbl <- read_sheet("practice", export_xlsx, sheet_names) %>%
  mutate(
    itemOrder = safe_numeric(itemOrder),
    correct = parse_flag(correct),
    elapsedMs = safe_numeric(elapsedMs),
    across(any_of(c("presentedAt", "submittedAt")), parse_time)
  )

events_tbl <- read_sheet("session_events", export_xlsx, sheet_names) %>%
  mutate(
    order = safe_numeric(order),
    timestamp = parse_time(timestamp)
  )

routing_tbl <- read_sheet("routing_summary", export_xlsx, sheet_names) %>%
  mutate(
    band = factor(tolower(band), levels = band_levels),
    across(any_of(c(
      "administeredTestlets", "administeredItems", "correctItems", "observedAccuracy"
    )), safe_numeric)
  ) %>%
  arrange(band)

linking_tbl <- read_sheet("linking_coeffs", export_xlsx, sheet_names) %>%
  mutate(
    band = factor(tolower(band), levels = band_levels),
    across(any_of(c("slope", "intercept", "correlation", "rmse", "calibrationSampleSize")), safe_numeric)
  ) %>%
  arrange(band)

testlet_variance_tbl <- read_sheet("testlet_variance", export_xlsx, sheet_names) %>%
  mutate(
    band = factor(tolower(band), levels = band_levels),
    across(any_of(c("positionInForm", "rawVariance", "linkedVariance", "linkSlope")), safe_numeric)
  ) %>%
  arrange(band, positionInForm)

if (has_ljt) {
  ljt_log_tbl <- read_sheet("ljt_log", export_xlsx, sheet_names) %>%
    mutate(
      phase = factor(phase, levels = c("practice", "main")),
      condition = factor(condition, levels = condition_levels),
      target_level = case_when(
        tolower(target_level) %in% band_levels ~ tolower(target_level),
        TRUE ~ as.character(target_level)
      ),
      target_level = factor(target_level, levels = c("practice", band_levels)),
      response_mode = as.character(response_mode),
      replay_enabled = parse_flag(replay_enabled),
      timeout_flag = parse_flag(timeout_flag),
      is_correct = parse_flag(is_correct),
      is_practice_extra = parse_flag(is_practice_extra),
      is_retry_original = parse_flag(is_retry_original),
      across(any_of(c(
        "trial_seq", "trial_in_phase", "audio_duration_ms",
        "first_audio_context_start_time_s", "audio_context_start_time_s",
        "first_audio_onset_at_ctx_s", "audio_onset_at_ctx_s",
        "first_audio_offset_at_ctx_s", "audio_offset_at_ctx_s",
        "last_audio_onset_at_ctx_s", "last_audio_offset_at_ctx_s",
        "deadline_at_ctx_s", "response_at_ctx_s", "response_value",
        "rt_from_offset_ms", "rt_from_first_offset_ms", "rt_from_last_offset_ms",
        "response_from_first_onset_ms", "response_from_last_onset_ms",
        "premature_click_count", "premature_replay_click_count",
        "audio_play_count_total", "audio_play_count_completed",
        "audio_replay_count"
      )), safe_numeric),
      across(any_of(c("started_at_iso", "settled_at_iso")), parse_time),
      valid_trial = if_else(is.na(invalidation_reason) | invalidation_reason == "", TRUE, FALSE),
      answered_trial = !is.na(response_value)
    ) %>%
    arrange(phase, trial_seq)

  ljt_summary_tbl <- read_sheet("ljt_summary", export_xlsx, sheet_names) %>%
    slice(1) %>%
    mutate(
      across(any_of(c(
        "n_trials_total", "n_trials_app", "n_trials_inapp", "n_correct_total",
        "n_correct_app", "n_correct_inapp", "n_hit_app", "n_fa_inapp",
        "n_timeout_app", "n_timeout_inapp", "H", "F", "d_primary",
        "c_primary", "d_excluding_timeouts", "raw_accuracy",
        "conditional_accuracy", "mean_rt_app_correct", "mean_rt_inapp_correct",
        "median_rt_app_correct", "median_rt_inapp_correct",
        "mean_rt_first_offset_all", "median_rt_first_offset_all",
        "mean_rt_last_offset_all", "median_rt_last_offset_all",
        "mean_rt_first_offset_correct", "median_rt_first_offset_correct",
        "mean_rt_last_offset_correct", "median_rt_last_offset_correct",
        "mean_audio_play_count_total", "median_audio_play_count_total",
        "mean_audio_replay_count", "median_audio_replay_count",
        "max_audio_replay_count", "practice_raw_accuracy", "practice_n_trials"
      )), safe_numeric)
    )

  ljt_meta_tbl <- read_sheet("ljt_session_meta", export_xlsx, sheet_names) %>%
    slice(1) %>%
    mutate(
      replay_enabled = parse_flag(replay_enabled),
      bluetooth_warning_shown = parse_flag(bluetooth_warning_shown),
      practice_extra_triggered = parse_flag(practice_extra_triggered),
      across(any_of(c(
        "audio_context_sample_rate", "audio_context_output_latency_ms",
        "audio_context_base_latency_ms", "headphone_check_attempts",
        "preload_total_files", "ljt_total_duration_s", "practice_accuracy",
        "practice_accuracy_original", "theta_pad_theta_hat",
        "theta_pad_width_used", "theta_pad_candidates_at_05",
        "theta_pad_candidates_at_10", "theta_pad_candidates_at_15",
        "theta_pad_needed", "theta_pad_chosen", "invalidated_trials_count",
        "events_tabswitch_count"
      )), safe_numeric),
      across(any_of(c(
        "preload_started_at", "preload_finished_at",
        "ljt_intro_entered_at", "ljt_main_started_at", "ljt_main_finished_at"
      )), parse_time)
    )
} else {
  ljt_log_tbl <- tibble()
  ljt_summary_tbl <- tibble()
  ljt_meta_tbl <- tibble()
}

summary_row <- summary_tbl[1, ]

session_overview_tbl <- tibble(
  指標 = c(
    "Session ID", "Participant", "CAT testlets", "CAT items",
    "Final theta", "Final SE", "Linked Rasch theta",
    "Estimated vocabulary size", "Visited bands",
    "Elapsed minutes", "Stop reason"
  ),
  値 = c(
    summary_row$sessionId,
    glue("{summary_row$studentId} / {summary_row$participantName}"),
    fmt_int(summary_row$administeredTestlets),
    fmt_int(summary_row$administeredItems),
    fmt_num(summary_row$theta),
    fmt_num(summary_row$se),
    fmt_num(summary_row$linkedRaschTheta),
    glue("{fmt_int(summary_row$estimatedVocabularySize)} ({fmt_int(summary_row$lowerVocabularySize)} - {fmt_int(summary_row$upperVocabularySize)})"),
    ifelse(is.na(summary_row$visitedBands) || summary_row$visitedBands == "", "-", summary_row$visitedBands),
    fmt_min(summary_row$sessionElapsedMs),
    ifelse(is.na(summary_row$stopReason) || summary_row$stopReason == "", "-", summary_row$stopReason)
  )
)

cat_band_tbl <- band_diag_tbl %>%
  left_join(
    routing_tbl %>% select(band, administeredTestlets, administeredItems, correctItems),
    by = "band"
  ) %>%
  mutate(
    band = toupper(as.character(band)),
    expectedAccuracyLabel = fmt_pct(expectedAccuracy),
    observedAccuracyLabel = fmt_pct(observedAccuracy),
    estimatedKnownWordsLabel = fmt_int(estimatedKnownWords)
  ) %>%
  select(
    band, itemCount, estimatedKnownWordsLabel, expectedAccuracyLabel,
    observedAccuracyLabel, administeredTestlets, administeredItems, correctItems
  )

event_summary_tbl <- events_tbl %>%
  count(type, sort = TRUE, name = "件数")

routing_plot_tbl <- testlet_log_tbl %>%
  filter(!is.na(order))

band_plot_tbl <- band_diag_tbl %>%
  select(band, expectedAccuracy, observedAccuracy) %>%
  pivot_longer(
    cols = c(expectedAccuracy, observedAccuracy),
    names_to = "metric",
    values_to = "accuracy"
  ) %>%
  filter(!is.na(accuracy)) %>%
  mutate(
    metric = recode(
      metric,
      expectedAccuracy = "Expected",
      observedAccuracy = "Observed"
    ),
    band = factor(toupper(as.character(band)), levels = toupper(band_levels))
  )

item_plot_tbl <- item_tbl %>%
  filter(!is.na(correct), !is.na(difficulty))

if (has_ljt && nrow(ljt_log_tbl) > 0) {
  ljt_main_tbl <- ljt_log_tbl %>%
    filter(phase == "main")

  ljt_main_valid_tbl <- ljt_main_tbl %>%
    filter(valid_trial)

  ljt_condition_tbl <- ljt_main_tbl %>%
    group_by(condition) %>%
    summarise(
      n_trials = n(),
      n_valid = sum(valid_trial, na.rm = TRUE),
      n_correct = sum(is_correct & valid_trial, na.rm = TRUE),
      invalidated = sum(!valid_trial, na.rm = TRUE),
      accuracy = mean(if_else(valid_trial, as.numeric(is_correct), NA_real_), na.rm = TRUE),
      mean_play_count = mean(if_else(valid_trial, audio_play_count_total, NA_real_), na.rm = TRUE),
      mean_replay_count = mean(if_else(valid_trial, audio_replay_count, NA_real_), na.rm = TRUE),
      median_rt_first = median(if_else(valid_trial & answered_trial, rt_from_first_offset_ms, NA_real_), na.rm = TRUE),
      median_rt_last = median(if_else(valid_trial & answered_trial, rt_from_last_offset_ms, NA_real_), na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(condition = fct_recode(condition, Appropriate = "appropriate", Inappropriate = "inappropriate"))

  ljt_level_tbl <- ljt_main_valid_tbl %>%
    filter(target_level %in% band_levels) %>%
    group_by(target_level) %>%
    summarise(
      n_trials = n(),
      accuracy = mean(as.numeric(is_correct), na.rm = TRUE),
      mean_replay_count = mean(audio_replay_count, na.rm = TRUE),
      median_rt_last = median(rt_from_last_offset_ms, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(target_level = factor(toupper(as.character(target_level)), levels = toupper(band_levels)))

  replay_dist_tbl <- ljt_main_valid_tbl %>%
    count(audio_replay_count, name = "n_trials") %>%
    arrange(audio_replay_count)

  rt_long_tbl <- ljt_main_valid_tbl %>%
    select(trial_seq, condition, rt_from_first_offset_ms, rt_from_last_offset_ms) %>%
    pivot_longer(
      cols = c(rt_from_first_offset_ms, rt_from_last_offset_ms),
      names_to = "basis",
      values_to = "rt_ms"
    ) %>%
    filter(!is.na(rt_ms)) %>%
    mutate(
      basis = recode(
        basis,
        rt_from_first_offset_ms = "First offset",
        rt_from_last_offset_ms = "Last offset"
      ),
      condition = fct_recode(condition, Appropriate = "appropriate", Inappropriate = "inappropriate")
    )

  timeline_tbl <- ljt_main_valid_tbl %>%
    select(trial_seq, condition, audio_replay_count, rt_from_last_offset_ms) %>%
    filter(!is.na(trial_seq))
} else {
  ljt_main_tbl <- tibble()
  ljt_main_valid_tbl <- tibble()
  ljt_condition_tbl <- tibble()
  ljt_level_tbl <- tibble()
  replay_dist_tbl <- tibble()
  rt_long_tbl <- tibble()
  timeline_tbl <- tibble()
}
```

# Workbook Overview

このレポートは workbook `r basename(export_xlsx)` を読み込み、CAT の routing・difficulty・帯域別成績に加えて、LJT シートが存在すれば replay 回数と反応時間も記述統計としてまとめます。絶対パスは `r export_xlsx` です。

```{r}
session_overview_tbl %>%
  gt() %>%
  cols_label(
    指標 = "Metric",
    値 = "Value"
  ) %>%
  tab_header(
    title = md("**Session Overview**")
  )
```

# CAT Descriptives

最終 CAT 推定値は **theta = `r fmt_num(summary_row$theta)`**、**SE = `r fmt_num(summary_row$se)`** です。推定語彙サイズは **`r fmt_int(summary_row$estimatedVocabularySize)` 語**、レンジは **`r fmt_int(summary_row$lowerVocabularySize)` - `r fmt_int(summary_row$upperVocabularySize)` 語** です。

```{r}
cat_band_tbl %>%
  gt() %>%
  cols_label(
    band = "Band",
    itemCount = "Items in Bank",
    estimatedKnownWordsLabel = "Estimated Known Words",
    expectedAccuracyLabel = "Expected Accuracy",
    observedAccuracyLabel = "Observed Accuracy",
    administeredTestlets = "Administered Testlets",
    administeredItems = "Administered Items",
    correctItems = "Correct Items"
  ) %>%
  tab_header(
    title = md("**Band-Level Overview**")
  )
```

```{r}
ggplot(band_plot_tbl, aes(band, accuracy, fill = metric)) +
  geom_col(position = position_dodge(width = 0.72), width = 0.62) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  scale_fill_manual(values = c("Expected" = "#4C78A8", "Observed" = "#F58518")) +
  labs(
    title = "Band-Level Accuracy: Expected vs Observed",
    x = NULL,
    y = "Accuracy",
    fill = NULL
  ) +
  theme_minimal(base_size = 12)
```

```{r}
ggplot(routing_plot_tbl, aes(order)) +
  geom_line(aes(y = selectionTheta, color = "Theta at selection"), linewidth = 0.8) +
  geom_point(aes(y = selectionDifficulty, color = "Selected difficulty"), size = 2.1) +
  scale_color_manual(values = c(
    "Theta at selection" = "#4C78A8",
    "Selected difficulty" = "#E45756"
  )) +
  labs(
    title = "CAT Routing Path on the Linked Scale",
    x = "Testlet order",
    y = "Logit scale",
    color = NULL
  ) +
  theme_minimal(base_size = 12)
```

```{r}
ggplot(item_plot_tbl, aes(difficulty, as.numeric(correct))) +
  geom_jitter(aes(color = level), width = 0.05, height = 0.06, alpha = 0.7, size = 2) +
  scale_y_continuous(
    breaks = c(0, 1),
    labels = c("Incorrect", "Correct"),
    limits = c(-0.1, 1.1)
  ) +
  labs(
    title = "Item Difficulty and Correctness",
    x = "Item difficulty",
    y = NULL,
    color = "Band"
  ) +
  theme_minimal(base_size = 12)
```

# LJT Descriptives

```{r results='asis'}
if (!has_ljt || !nrow(ljt_main_tbl)) {
  cat("> この workbook には `ljt_log / ljt_summary / ljt_session_meta` がないため、LJT セクションは省略されます。")
}
```

```{r}
if (has_ljt && nrow(ljt_summary_tbl)) {
  ljt_row <- ljt_summary_tbl[1, ]

  tibble(
    指標 = c(
      "Response mode", "Replay enabled", "Main trials", "d-prime",
      "Hit rate", "False-alarm rate", "Raw accuracy",
      "Mean play count", "Mean replay count",
      "Median RT from first offset", "Median RT from last offset"
    ),
    値 = c(
      ljt_meta_tbl$response_mode[[1]],
      ifelse(isTRUE(ljt_meta_tbl$replay_enabled[[1]]), "TRUE", "FALSE"),
      fmt_int(ljt_row$n_trials_total),
      fmt_num(ljt_row$d_primary),
      fmt_pct(ljt_row$H),
      fmt_pct(ljt_row$F),
      fmt_pct(ljt_row$raw_accuracy),
      fmt_num(ljt_row$mean_audio_play_count_total, digits = 2),
      fmt_num(ljt_row$mean_audio_replay_count, digits = 2),
      fmt_ms(ljt_row$median_rt_first_offset_all),
      fmt_ms(ljt_row$median_rt_last_offset_all)
    )
  ) %>%
    gt() %>%
    cols_label(
      指標 = "Metric",
      値 = "Value"
    ) %>%
    tab_header(
      title = md("**LJT Overview**")
    )
}
```

```{r}
if (has_ljt && nrow(ljt_condition_tbl)) {
  ljt_condition_tbl %>%
    mutate(
      accuracy = fmt_pct(accuracy),
      mean_play_count = fmt_num(mean_play_count, digits = 2),
      mean_replay_count = fmt_num(mean_replay_count, digits = 2),
      median_rt_first = fmt_ms(median_rt_first),
      median_rt_last = fmt_ms(median_rt_last)
    ) %>%
    gt() %>%
    cols_label(
      condition = "Condition",
      n_trials = "Trials",
      n_valid = "Valid",
      n_correct = "Correct",
      invalidated = "Invalidated",
      accuracy = "Accuracy",
      mean_play_count = "Mean Play Count",
      mean_replay_count = "Mean Replay Count",
      median_rt_first = "Median RT (First Offset)",
      median_rt_last = "Median RT (Last Offset)"
    ) %>%
    tab_header(
      title = md("**LJT by Condition**")
    )
}
```

```{r}
if (has_ljt && nrow(replay_dist_tbl)) {
  ggplot(replay_dist_tbl, aes(audio_replay_count, n_trials)) +
    geom_col(fill = "#54A24B", width = 0.7) +
    scale_x_continuous(breaks = sort(unique(replay_dist_tbl$audio_replay_count))) +
    labs(
      title = "Replay Count Distribution (Main LJT)",
      x = "Replay count",
      y = "Number of trials"
    ) +
    theme_minimal(base_size = 12)
}
```

```{r}
if (has_ljt && nrow(rt_long_tbl)) {
  ggplot(rt_long_tbl, aes(condition, rt_ms, fill = basis)) +
    geom_boxplot(outlier.alpha = 0.2, width = 0.65, position = position_dodge(width = 0.7)) +
    scale_y_continuous(labels = comma_format()) +
    scale_fill_manual(values = c("First offset" = "#4C78A8", "Last offset" = "#E45756")) +
    labs(
      title = "LJT Reaction Time by Condition and Reference Point",
      x = NULL,
      y = "RT (ms)",
      fill = NULL
    ) +
    theme_minimal(base_size = 12)
}
```

```{r}
if (has_ljt && nrow(timeline_tbl)) {
  timeline_long_tbl <- timeline_tbl %>%
    mutate(condition = fct_recode(condition, Appropriate = "appropriate", Inappropriate = "inappropriate")) %>%
    pivot_longer(
      cols = c(audio_replay_count, rt_from_last_offset_ms),
      names_to = "metric",
      values_to = "value"
    ) %>%
    mutate(
      metric = recode(
        metric,
        audio_replay_count = "Replay count",
        rt_from_last_offset_ms = "RT from last offset (ms)"
      )
    )

  ggplot(timeline_long_tbl, aes(trial_seq, value, color = condition)) +
    geom_line(alpha = 0.7) +
    geom_point(size = 1.8) +
    facet_wrap(~ metric, scales = "free_y", ncol = 1) +
    labs(
      title = "Trial-by-Trial LJT Behavior",
      x = "Main-trial order",
      y = NULL,
      color = "Condition"
    ) +
    theme_minimal(base_size = 12)
}
```

```{r}
if (has_ljt && nrow(ljt_level_tbl)) {
  ljt_level_tbl %>%
    mutate(
      accuracy = fmt_pct(accuracy),
      mean_replay_count = fmt_num(mean_replay_count, digits = 2),
      median_rt_last = fmt_ms(median_rt_last)
    ) %>%
    gt() %>%
    cols_label(
      target_level = "Target Level",
      n_trials = "Trials",
      accuracy = "Accuracy",
      mean_replay_count = "Mean Replay Count",
      median_rt_last = "Median RT (Last Offset)"
    ) %>%
    tab_header(
      title = md("**LJT by Target Level**")
    )
}
```

# Session Quality

CAT 側では中断イベントが **`r fmt_int(summary_row$interruptionEvents)` 件**、ブラウザ戻り操作が **`r fmt_int(summary_row$browserBackAttempts)` 回**、復帰イベントが **`r fmt_int(summary_row$restoreEvents)` 回** 記録されています。

```{r}
if (nrow(event_summary_tbl)) {
  event_summary_tbl %>%
    gt() %>%
    cols_label(
      type = "Event Type",
      件数 = "Count"
    ) %>%
    tab_header(
      title = md("**Session Events**")
    )
}
```

```{r}
if (nrow(event_summary_tbl)) {
  ggplot(event_summary_tbl, aes(fct_reorder(type, 件数), 件数)) +
    geom_col(fill = "#B279A2") +
    coord_flip() +
    labs(
      title = "Session Event Frequency",
      x = NULL,
      y = "Count"
    ) +
    theme_minimal(base_size = 12)
}
```

```{r}
if (has_ljt && nrow(ljt_meta_tbl)) {
  tibble(
    指標 = c(
      "Headphone check attempts",
      "Headphone result",
      "Connection estimate",
      "Output latency (ms)",
      "Bluetooth warning shown",
      "LJT duration (s)",
      "Invalidated LJT trials",
      "Practice extra triggered"
    ),
    値 = c(
      fmt_int(ljt_meta_tbl$headphone_check_attempts[[1]]),
      ljt_meta_tbl$headphone_check_result[[1]],
      ljt_meta_tbl$connection_type_estimate[[1]],
      fmt_num(ljt_meta_tbl$audio_context_output_latency_ms[[1]], digits = 1),
      ifelse(isTRUE(ljt_meta_tbl$bluetooth_warning_shown[[1]]), "TRUE", "FALSE"),
      fmt_num(ljt_meta_tbl$ljt_total_duration_s[[1]], digits = 1),
      fmt_int(ljt_meta_tbl$invalidated_trials_count[[1]]),
      ifelse(isTRUE(ljt_meta_tbl$practice_extra_triggered[[1]]), "TRUE", "FALSE")
    )
  ) %>%
    gt() %>%
    cols_label(
      指標 = "Metric",
      値 = "Value"
    ) %>%
    tab_header(
      title = md("**LJT Session Meta**")
    )
}
```

# Render

このドキュメントは次のように render できます。

```bash
quarto render Analysis/uvlt_export_descriptives.qmd \
  -P export_xlsx=/absolute/path/to/export_workbook.xlsx
```
